Equalizer Programming Guide

### 2007-12-20 Developer/ProgrammingGuide/paper.tex
Documentation updates for last change
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.6 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    1.1.2   & Nov 19, 2007 & Minor improvements based on feedback\\
    1.1.3   & Nov 23, 2007 & Add OpenGL extension handling\\
    1.1.4   & Nov 26, 2007 & Changes caused by removal of glX event thread\\
    1.1.5   & Dec 10, 2007 & NodeFactory API changes\\
    1.1.6   & Dec 17, 2007 & Add Scalable Rendering chapter\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

The OM is a template class. The template type is the key used to
identify objects. The same key is used by all contexts to get the
OpenGL name of an object. In \textsf{eqPly}, a key of type \textsf{const
  void *} is used. The rendering code uses the address of the data item
to be rendered as the key to obtain the associated OpenGL object.

All objects managed by the OM are reference counted. If an application
releases the objects properly, they are automatically de-allocated. It
is also possible to manually manage de-allocation of objects, which
might be more convenient in some cases.

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.7 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    1.1.2   & Nov 19, 2007 & Minor improvements based on feedback\\
    1.1.3   & Nov 23, 2007 & Add OpenGL extension handling\\
    1.1.4   & Nov 26, 2007 & Changes caused by removal of glX event thread\\
    1.1.5   & Dec 10, 2007 & NodeFactory API changes\\
    1.1.6   & Dec 17, 2007 & Add Scalable Rendering chapter\\
    1.1.7   & Dec 20, 2007 & Per-window object manager changes\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

The OM is a template class. The template type is the key used to
identify objects. The same key is used by all contexts to get the
OpenGL name of an object.

Each \textsf{eq::Window} has an object manager with the key type
\textsf{const void*} for as long as it has an OpenGL context. The OM is
shared between all windows of a pipe, if the windows are created using
the default \textsf{configInit} functions. If the window is created by
the application, the OM is not shared since no assumption can be made
about OpenGL context sharing. Later version of Equalizer will introduce
an API to configure OpenGL context sharing, and therefore OM sharing, for
application-created windows.

\textsf{eqPly} uses the window's object manager in the rendering code to
obtain the OpenGL objects for a given data item. The address of the data
item to be rendered is used as the key. All objects managed by the OM
are reference counted. If an application releases the objects properly,
they are automatically de-allocated. It is also possible to manually
manage de-allocation of objects, which might be more convenient in some
cases.
